\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-06-27 eg6-letters/NIM/EG6_RTPC_NIM.tex
Typo

The primary data sample used for calibration and performance assessment of the
RTPC was elastic scattering with a 1.2 GeV electron beam.  The electron's momentum
and direction is measured with CLAS, which uniquely determines the expected recoiling
$^4$He kinematics.  Matching requirements between reconstructed and expected $z$-vertex
and direction of the RTPC track provides a clean selection of elastically-scattered
$^4$He, showin in Fig.~\ref{fig:w}.

>>>>

The primary data sample used for calibration and performance assessment of the
RTPC was elastic scattering with a 1.2 GeV electron beam.  The electron's momentum
and direction is measured with CLAS, which uniquely determines the expected recoiling
$^4$He kinematics.  Matching requirements between reconstructed and expected $z$-vertex
and direction of the RTPC track provides a clean selection of elastically-scattered
$^4$He, shown in Fig.~\ref{fig:w}.
